---
title: "Plotting with ggplot"
output:
  html_document:
    toc: yes
    toc_float: yes
---

This is a worked set of answers to the Babraham ggplot course

```{r}
library(tidyverse)
```


Exercise 1 - Simple Plots and Lines
===================================

Weight Chart
------------
Load the data from ```weight_chart.tsv```

```{r}
read_tsv("weight_chart.txt") -> weight
weight
```

Draw a scatterplot of the the Age vs the Weight.


```{r}
weight %>%
  ggplot(aes(x=Age, y=Weight)) +
  geom_point()
```

Make all of the points filled with blue and have a size of 3.  These are both static aesthetics so they will go into the geometry function rather than the aes call of the ggplot function.

```{r}
weight %>%
  ggplot(aes(x=Age, y=Weight)) +
  geom_point(color="blue", size=3)
```

Change the geometry to geom_line to draw a line graph.

```{r}
weight %>%
  ggplot(aes(x=Age, y=Weight)) +
  geom_line()
```

Combine the two plots to give a point and line graph.  This will use two geometry layers.  We do the line plot first so that the points sit on top of the lines and not beneath them.

```{r}
weight %>%
  ggplot(aes(x=Age, y=Weight)) +
  geom_line() +
  geom_point(color="blue", size=3)
```

Chromosome Position
-------------------
Load the data from ```chromosome_position_data.txt```

```{r}
read_tsv("chromosome_position_data.txt") -> chr.pos
chr.pos
```

Gather the data into tidy format.  This is needed because at the moment we could plot out any individual dataset, or do a satterplot of one dataset against another, but if we want to plot all 3 datasets against the position then we'll need the data for all 3 datasets to be in the same column.

```{r}
chr.pos %>%
  gather(key=sample, value=measure, -Position) -> chr.pos

chr.pos
```

Draw a line graph of the position vs the measure splitting the different samples by colour.  Make the lines slightly thicker than default.

```{r}
chr.pos %>%
  ggplot(aes(x=Position, y=measure, color=sample)) +
  geom_line(size=1)
```

Genomes
-------

Load the ```genomes.csv``` file and use separate to turn the Groups column into Domain, Kingdom and Class.

```{r}
read_csv("genomes.csv") -> genomes
head(genomes)
```

We can see that Groups is a combined value of 3 different values which we need to split apart

```{r}
genomes %>%
  separate(Groups, into=c("Domain","Kingdom","Class"), sep=";") -> genomes

genomes
```

Plot a point graph of log10 Size vs Chromosome and colour it by Domain

```{r}
genomes %>%
  ggplot(aes(x=log10(Size), y=Chromosomes, color=Domain)) +
  geom_point()
```


Exercise 2 - Barplots and Distributions
=======================================

small_file
----------

```{r}
read_tsv("small_file.txt") -> small.file

small.file
```

Plot a barplot of the lenghts of each sample from category A

```{r}
small.file %>%
  filter(Category == "A")
```









